Dynamical Properties of Molecular Cloud Complexes in Galaxies at the Epoch of Reionization

### 2019-03-27 WRITEUP/ms.tex
revisions and comments to 4.2

Note that we impose the additional constraint that an identified
structure must be composed of at least 10 cells. We caution that an
important caveat of such a constraint is that we can only examine the
parameter space of cloud complexes of 
%mm typical size
   radius 
$R\gtrsim 60$\,pc, because of the resolution limit of the simulation.

@@

% Molecular clouds are the natal place for \SF, their structure and dynamics hold important clues to understanding
% the mechanisms and physics of formation and evolution of molecular structures and \SF.
Upon identifying the molecular structures, we extract properties such as the gas mass ($M_{\rm cl}$), effective size ($R$), Mach number ($\mathcal{M}$), r.m.s. velocity dispersion ($\sigma$), and gas surface density ($\Sigma_{\rm gas}$) to examine their dynamics.

The mass of an MCC is calculated from the uniformly-gridded 3D density field, integrating over the MCC volume $V$. The effective size is defined assuming spherical geometry, i.e. $R \equiv (3 V /4 \pi)^{1/3}$.
%
The velocity dispersion of MCCs is calculated from non-thermal velocity dispersion ($\sigma_{\rm NT}$) and thermal sound speed ($c_s$):
\begin{equation}
\sigma^2 = \sigma_{\rm NT}^2 + c_s^2.
\label{eqn:veldisp}
\end{equation}
%
In \obs of MCC, the linewidths contribution of dense gas contribution is larger then the one from the diffuse gas. We therefore calculate each term on the RHS of Equation~\ref{eqn:veldisp} as a density-weighted quantity. For instance, the non-thermal velocity dispersion is calculated as follows:
\begin{equation}
\sigma_{\rm NT}^2 = \frac{1}{{3}}\frac{\sum_{i} \rho_i \left|\mathbf{v}_i - \mathbf{\bar v}\right|^2}{\sum_i \rho_i}\,,
\end{equation}
where the sum is done for the cells composing each MCC.
%
The local sound speed of all identified molecular complexes is much smaller than their turbulent velocities\footnote{Velocity dispersions calculated from velocity field are comparable to those calculated from the pressure field, indicating that contribution from shear is unlikely to dominating the velocity dispersions reported here.\label{ftn:veldisp}}. On average, the Mach number of the MCCs is  $\mathcal{M} = \sigma_{\rm NT}/c_s\simeq 50$. This is consistent with the global analysis done on \flower by \citet{Vallini18a}.

We show in \Fig{dist} the MCC distribution in terms of their molecular gas mass, radius, and gas mass fraction, which we define as
\begin{equation}
f_{\rm gas} = \frac{M_{\rm cl}} {\left(M_{\rm cl} + M_\star\right)},
\end{equation}
where $M_\star$ is the stellar mass within the MCC volume.
%
We note that the distributions vary for different evolutionary stages of \flower. The highest density threshold of $n_{\rm cut}$\eq31.62\,\cc yields a minimum MCC mass of the order of 10$^{5.5}$\,\Msun for the densest MCC.
%
We find $\sim$10$-$13 MCCs with masses exceeding 10$^8$\,\Msun across all the evolutionary stages considered in this work, for each  $n_{\rm cut}$ value. \AF{This is true only for low $n_{cut}$? Why in Fig. do you show the valu 18.96 instead?} \DL{MCCs w/ Mcl $>$10$^8$\,\Msun is the case for each ncut.} Such massive clouds correspond to the galaxy molecular disk, that is identified as a single component for low $n_{\rm cut}$. The mass of the MCCs identified ranges between $M_{\rm cl}\simeq$10$^{5.5-8.5}$\,\Msun, consistent with those observed in \z$\sim$2 galaxies in rest-frame UV and optical light \citep{Elmegreen07a, Elmegreen09a}. \AF{you do not comment on $R$ and $f_{gas}$ here..Also, what is the total number of MCCs?}

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/minmaxNcut_basicDistributions.pdf}
\caption{Distributions of mass (left), size (middle), and gas mass fraction (right) of MCCs identified using the lowest $n_{\rm cut}$ (top panels) and $n_{\rm ncut}$\eq18.96\,\cc (bottom panels).
Note that the scale shown on the y-axes are different between the top and bottom panels, as less MCCs are identified at higher $n_{\rm cut}$.
\label{fig:dist}}
\end{figure*}

>>>>

Note that we impose the additional constraint that an identified
structure must be composed of at least 10 cells. We caution that an
important caveat of such a constraint is that we can only examine the
parameter space of cloud complexes of 
%mm typical size $R\gtrsim 60$\,pc [revised assuming spherical MCCs
%per Sect 4.2]
   radius $R\gtrsim 40$\,pc,
because of the resolution limit of the simulation.

@@

% Molecular clouds are the natal place for \SF, their structure and dynamics hold important clues to understanding
% the mechanisms and physics of formation and evolution of molecular structures and \SF.
Upon identifying the molecular structures, we extract properties such
as the gas mass $M_{\rm cl}$, effective size $R$, Mach number
$\mathcal{M}$, r.m.s. velocity dispersion $\sigma$
, and gas surface density $\Sigma_{\rm gas}$ to examine their dynamics.

The mass of an MCC is calculated from the uniformly-gridded 3D density field, integrating over the MCC volume $V$. The effective size is defined assuming spherical geometry, i.e. $R \equiv (3 V /4 \pi)^{1/3}$.
%
The velocity dispersion of MCCs is calculated from non-thermal
velocity dispersion $\sigma_{\rm NT}$ and thermal sound speed $c_s$ as
\begin{equation}
\sigma^2 = \sigma_{\rm NT}^2 + c_s^2.
\label{eqn:veldisp}
\end{equation}
%
In \obs of MCCs, the linewidth contribution of dense gas 
exceeds that from the diffuse gas. We therefore calculate each term on
the right-hand side of Equation~\ref{eqn:veldisp} as a density-weighted quantity. For instance, the non-thermal velocity dispersion is calculated as follows:
\begin{equation}
\sigma_{\rm NT}^2 = \frac{1}{{3}}\frac{\sum_{i} \rho_i \left|\mathbf{v}_i - \mathbf{\bar v}\right|^2}{\sum_i \rho_i}\,,
\end{equation}
where the sum is done for the cells composing each MCC.
%
The local sound speed of all identified molecular complexes is much
smaller than their turbulent velocities\footnote{Velocity dispersions
  calculated from velocity field are comparable to those calculated
  from the pressure field 
%mm
    \MM{The turbulent pressure field has not been
    mentioned in section 3, so you'll need to add a sentence there
    mentioning its presence and behavior to mention it here}, 
indicating that contribution from shear is unlikely to dominate the velocity dispersions reported here.\label{ftn:veldisp}}. On average, the Mach number of the MCCs is  $\mathcal{M} = \sigma_{\rm NT}/c_s\simeq 50$. This is consistent with the global analysis done on \flower by \citet{Vallini18a}.

We show in \Fig{dist} the MCC distribution in terms of their molecular gas mass, radius, and gas mass fraction, which we define as
\begin{equation}
f_{\rm gas} = \frac{M_{\rm cl}} {\left(M_{\rm cl} + M_\star\right)},
\end{equation}
where $M_\star$ is the stellar mass within the MCC volume.
%
We note that the distributions vary for different evolutionary stages of \flower. The highest density threshold of $n_{\rm cut}$\eq31.62\,\cc yields a minimum MCC mass of the order of 10$^{5.5}$\,\Msun for the densest MCC.
%
We find $\sim$10--13 MCCs with masses exceeding 10$^8$\,\Msun across
all the evolutionary stages considered in this work, for each  $n_{\rm
  cut}$ value. \AF{This is true only for low $n_{cut}$? Why in Fig. do
  you show the valu 18.96 instead?} \DL{MCCs w/ Mcl $>$10$^8$\,\Msun
  is the case for each ncut.} \MM{I am afraid I am also confused by
  this, for two reasons.  First, if I understand the Figure, the
  highest $n_{\rm cut}$ shows no such large MCCs at any time.  Second,
  back in section 3, the H$_2$ mass of \flower was given as 5\E7
  \Msun, precluding the existence of even a single 10$^8$ \Msun
  cloud.} Such massive clouds correspond to the molecular disk of the
galaxy, which is identified as a single component for low $n_{\rm
  cut}$. The mass of the MCCs identified ranges between $M_{\rm
  cl}\simeq$10$^{5.5-8.5}$\,\Msun, consistent with those observed in
\z$\sim$2 galaxies in rest-frame UV and optical light
\citep{Elmegreen07a, Elmegreen09a}. \AF{you do not comment on $R$ and
  $f_{gas}$ here..Also, what is the total number of MCCs?} \MM{In the
  high-density plot, it looks like you have quite a number of
  unresolved clouds with $R < 40$~pc. Any idea what's going on there?}

\begin{figure*}[htbp]
\centering
\includegraphics[trim=0 0 0 0, clip, width=\textwidth]{\figpath/minmaxNcut_basicDistributions.pdf}
\caption{Distributions of mass (left), size (middle), and gas mass
  fraction (right) of MCCs identified using the lowest $n_{\rm cut}$
  (top panels) and $n_{\rm ncut}$\eq18.96\,\cc (bottom panels)
%mm
      over all times analyzed here.
Note that the scalesshown on the $y$-axes are different between the top
and bottom panels, as fewer MCCs are identified at higher $n_{\rm
  cut}$. \MM{Put labels on the y-axis (maybe just $N$ or some such). Tick marks should point inwards
  rather than outwards.  I'd suggest putting the $n_{\rm cut}$ labels
  on the left panels following the style of the previous figure (and
  drop the brackets around the unit there). The $R$ axis could
  reasonably be pulled in to 250 pc, providing a bit more dynamic
  range at the low end.}
\label{fig:dist}}
\end{figure*}
